% !TEX program = XeLaTeX
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Praveen Kumar }{Pendyala}
       {Android developer | Linux enthusiast | Web hobbist}

% In the aside, each new line forces a line break
\begin{aside}
  \section{Info}
    DOB: 26.10.1992
    \href{http://pkp.io}{pkp.io}
    \href{http://github.com/praveendath92}{github/praveendath92}
  \section{Contact}
    \href{mailto:m@praveen.xyz}{m@praveen.xyz}
    (+49) 176-833-55188
    ~
    Moltkestr. 15
    64295 Darmstadt
    Germany
    ~
  \section{Skills}
    \noindent\rule{3cm}{0.1pt}
  \section{Programming}
    Java, PHP, Kernel C, Python, JavaScript, Shell, Verilog
  \section{Web}
    AngularJs, HTML5, CSS3, REST APIs, Bootstrap, MVCs
  \section{Android}
    Retrofit, Volley, Picasso, Material Design, Play Services
  \section{Tools}
    Git, SVN, Asterisk, Xilinx ISE, Jekyll, \LaTeX, Moodle, Wordpress
  \section{Platforms}
    Linux, Windows, Mac OSX, Beaglebone, Google App Engine
\end{aside}


\section{Education}

\begin{entrylist}
  \entry
    {since 2014}
    {Masters, {\normalfont Distributed Software Systems}}
    {Technische Universität Darmstadt}
    {}%GPA: 1.88 (converted 4.02 / 5.0)}
  \entry
    {2010–2014}
    {Bachelors, {\normalfont Electrical Engineering}}
    {Indian Institute of Technology Bombay}
    {}%GPA: 7.49 / 10}
  \entry
    {2008–2010}
    {Higher Secondary}
    {Vijaya Ratna Junior College, Hyderabad}
    {}%GPA: 7.49 / 10}
\end{entrylist}

\section{Experience}

\begin{entrylist}
  \entry
    {since 2014}
    {Center for Advanced Security Research Darmstadt}
    {Research Assistant}
    {\emph{Working in Cloud, Android and Mobile security.}}
  \entry
    {05–08 2015}
    {Google Summer of Code}
    {Supporting mentor}
    {\emph{Linux drivers for remote access from Android.}}
  \entry
    {05–08 2014}
    {Google Summer of Code}
    {Developer}
    {\emph{Developed kernel display driver for remote access to Linux from Android.}}
  \entry
    {05–07 2013}
    {Rice Univeristy}
    {Research Internship}
    {\emph{Implemented a dual-core Physically Unclonable Function.}}
\end{entrylist}

\section{Publications}
\begin{entrylist}
  \entry
    {2014}
    {PUFatt: Embedded Platform Attestation Based on Novel Processor-Based PUFs}
    {Best paper candidate, Design Automation Conference}
    {\emph{Kong, J., F. Koushanfar, P. K. Pendyala, A. - R. Sadeghi, and C. Wachsmann}}
\end{entrylist}

\section{Achievements}
\begin{itemize}
  \item A. Richard Newton Young Student Fellow Award, DAC 2014, San Francisco
  \item All India category Rank 1 among 470,000 students in IIT JEE 2010
  \item All India category Rank 1 in Indian Institute of Space Technology Admission Test, 2010
\end{itemize}
~

\section{Projects}
\begin{entrylist}
  \entry
    {since 2012}
    {MDroid - Moodle for Android}
    {Android, Githooks, REST, Markdown}
    {\emph{Creator and maintainer. 73,000+ downloads. Top app for Moodle.}}
  \entry
    {2015}
    {\href{https://coursestats.de}{Coursestats.de}}
    {PHP, AngularJs, GAE, Python, Material Design, MySQL}
    {\emph{Course statistics and reviews from student community at TU Darmstadt.}}
  \entry
    {2015}
    {Omnishare}
    {Android, Cryptography, Dropbox Core APIs}
    {\emph{Client side encryption of Cloud data with easy-to-use file sharing support.}}
  \entry
    {2014}
    {Android accessory driver}
    {Linux Kernel, Android accessory}
    {\emph{Kernel driver to set any Android device into Accessory (ADK) mode.}}
  \entry
    {2014}
    {Programmable Delay Logic}
    {Verilog, Xilinx ISE, Virtex 5}
    {\emph{Implemented PDL on virtex 5 FPGA. Configurable precision of 10 picoseconds.}}
  \entry
    {2013}
    {Tum Tum Tracker, IIT Bombay}
    {Android, Google Maps}
    {\emph{Android application to track internal transportation vehicles at IIT Bombay.}}
%   \entry
%     {2013}
%     {Mugshot}
%     {Android, Device Administration, Dropbox API}
%     {\emph{Auto picture taking on device unlock fails. Stood first in Institute Hacknight.}}
%   \entry
%     {2012}
%     {Aagomani Website}
%     {JavaScript, Ajax, CSS, PHP}
%     {\emph{Website for annual festival of Dept. of Electrical Engineering, IIT Bombay.}}
\end{entrylist}

\end{document}
